 \chapter{History of Grundfos} \label{ch:History of Grundfos}

In 1945 Poul Due Jensen founded what later became Grundfos in 1967, he is by many seen as a technical genius. He started in his basement with two employees, here he started by installing plumbings and doing blacksmith work.\\

Once Poul Due was asked by a local farmer if he could install a motor driven water pump on his farm. He searched for such a pump but, there was none available on market due to the crisis after the second world war. 
He then created his first pump known as "The Pig", which he engineered from scratch, afterwards his production expanded quickly. 
One of the inventions of Poul's was the Grundfos-carousel, this moves components around two different workstations, some of which are still running 24 hours a day.\\

Poul also gave Grundfos some principles to follow, which were social responsibility towards employees and the local community.

The business kept running and expanded. Now there are 19.000 employees, which produce an estimated of 16 million pumps yearly.\\
One thing worth mentioning is the values which the company is built around.\\

\begin{itemize}
   
\item 1. Sustainability.\\ This value is based on producing safe climate solutions and reducing nature resources spent.\\
\item 2. Credibility.\\ This value helps both parts, the buyer and the company. As a big company it is crucial to keep the customers satisfied, and upholding what is promised. Hereby Grundfos use a lot of energy to keep it simple and down to the earth with facts.\\
\item 3. Ambitious.\\ To keep both the staff and the management of Grundfos occupied they strive to come up with the best solutions without jumping the fence where it's lowest.\\
\end{itemize}
Grundfos is currently using, and further implementing robotic aid to help perform various tasks and streamline the production. An automated sorting system, using robot arms to move around boxes of parts, is currently under development and testing. Grundfos is however, already using the Kuka KR30 robot to feed parts directly into machinery, which was previously an expensive and operator intensive process. Among other, these are some of the reasons Grundfos is considered an innovative, leading company in their field. \cite{1Grundfos}

\subsection{Factory of the Future}

The production of Grundfos is based on linking it to the costumers. The red line between the early stages of the pump and the service is based on how many features that is implemented to help the consumers to both save money and use less water. This is the reason Grundfos is the leading company.
The work-process of the pump is split in to different sections of experts handling, the mechanics, the hydraulics, the marketing and so on.\\


