\section{History of Grundfos} \label{ch:History of Grundfos}

In 1945 Poul Due Jensen founded what later became Grundfos in 1967. He started from his basement, where he did plumbings and blacksmith work, and had two employees\cite{documentray}.\\
\\
Once Poul Due was asked by a local farmer if he could install a motor driven water pump at his farm. He searched for such a pump, but there was none available on market due to the crisis after the second world war. 
He then created his first pump known as "The Pig", which he engineered from scratch, afterwards his production expanded quickly. 
One of Poul's inventions was the Grundfos-carousel. This carousel moves components around two different workstations, some of which are still running 24 hours a day\cite{documentray}.\\
\\
Poul gave Grundfos some founding principles to follow, which were social responsibilities towards employees and the local community.
The business kept expanding, and now there are 19.000 employees, which produce approximately 16 million pumps per year\cite{1Grundfos}.\\
\\
Worth mentioning is one of their core values which the company is built around.\\

   
\paragraph{Sustainability.} Grundfos is following the goals, which are set in the UN sustainability goals, number 6 \cite{Ggoal6}. These goals are meant to lower the water stress level around the world, and to provide clean water efficiently \cite{goal6}.\\
%\item 2. Credibility.\\ This value helps both parts, the buyer and the company. As a big company it is crucial to keep the customers satisfied, and upholding what is promised.\\
%\item 3. Ambitious.\\ At Grundfos they strive to come up with the best solutions without cutting corners.\\
Grundfos is currently using, and further implementing robotic aid to help perform various tasks and streamline the production. With 250 robots and counting, an automated sorting system using robotic manipulators to move parts around, is currently under development and testing. They are a perfect example of how robots are enhancing factory work-flow, and improving the speed and efficiency.  Grundfos is however, already using the KUKA KR30 robot to feed parts directly into machinery, which was previously an expensive and operator intensive process. Among other, these are some of the reasons Grundfos is considered an innovative leading company in their field\cite{1Grundfos},\cite{Grundfosrobot}. 

%\subsection{Factory of the Future}

%Factory of the Future is based on the early stage of the production to shipment and service of the product, linking all the above to fit the customers need.\\
%The red line between the early stages of the pump and the service is based on how many features that is implemented to help the consumers to both save money and use less water. This is the reason Grundfos is the leading company.
%The work-process of the pump is split in to different sections of experts handling the mechanics, hydraulics, marketing etc.\\


